Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data

### 2022-11-12 paper/manuscript.Rmd
bookmark me!

Byron C. Jaeger, PhD,^1^ 
Ligong Chen, PhD,^2^
Kathryn Foti,^2^
Shakia T. Hardy,^2^
Adam P. Bress, PharmD, MS,^3,4^ 
Sean P. Kane, PharmD, BCPS,^5^
Jennifer S. Herrick, MS,^3,6^
Catherine Derington, PharmD, MS,^7^ 
Bharat Poudel, MSPH,^2^
Ashley Christenson, BS,^2^ 
Lisandro D. Colantonio, MD, PhD,^2^
Paul Muntner, PhD,^2^

@@

**Results**: The estimated mean systolic blood pressure (BP) declined from 123 mmHg in 1999-2000 to 120 mmHg in 2009-2010 and increased to 123 mmHg in 2017-2020. The age-adjusted prevalence of hypertension (i.e., systolic BP ≥130 mmHg, diastolic BP ≥80 mmHg or self-reported antihypertensive medication use) was 47.9% in 1999-2000, 43.0% in 2009-2010, and 44.7% in 2017-2020. In 2017-2020, 115.3 million US adults had hypertension. The age-adjusted prevalence of controlled BP, defined by the 2017 American College of Cardiology/American Heart Association BP guideline, among US adults with hypertension was 9.7% in 1999-2000, 25.0% in 2013-2014, and 21.9% in 2017-2020. After age-adjustment and among non-pregnant US adults who self-reported taking antihypertensive medication, 27.6%, 48.5%, and 43.0% had controlled BP in 1999-2000, 2013-2014, and 2017-2020, respectively.

>>>>

Byron C. Jaeger, PhD,^1^ 
Ligong Chen, PhD,^2^
Kathryn Foti, PhD, MPH^2^
Shakia T. Hardy,^2^
Adam P. Bress, PharmD, MS,^3,4^ 
Sean P. Kane, PharmD, BCPS,^5^
Jennifer S. Herrick, MS,^3,6^
Catherine Derington, PharmD, MS,^7^ 
Bharat Poudel, MSPH,^2^
Ashley Christenson, BS,^2^ 
Lisandro D. Colantonio, MD, PhD,^2^
Paul Muntner, PhD,^2^

@@

**Results**: The estimated mean systolic blood pressure (BP) declined from 123 mmHg in 1999-2000 to 120 mmHg in 2009-2010 and increased to 123 mmHg in 2017-2020. The age-adjusted prevalence of hypertension (i.e., systolic BP ≥130 mmHg, diastolic BP ≥80 mmHg or self-reported antihypertensive medication use) was 47.9% in 1999-2000, 43.0% in 2009-2010, and 44.7% in 2017-2020. In 2017-2020, 115.3 million US adults had hypertension. The age-adjusted prevalence of controlled BP, defined by the 2017 American College of Cardiology/American Heart Association BP guideline, among non-pregnant US adults with hypertension was 9.7% in 1999-2000, 25.0% in 2013-2014, and 21.9% in 2017-2020. After age-adjustment and among non-pregnant US adults who self-reported taking antihypertensive medication, 27.6%, 48.5%, and 43.0% had controlled BP in 1999-2000, 2013-2014, and 2017-2020, respectively.
